Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-06-19 Papers/ViscousInstabilities/Bank2/article_figure1_Feb.tex
keeping the original February files safe

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.5\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_60.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_90.pdf} }
      \hbox{\hspace{3.0cm} (a) t=0.29s \hspace{4.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
      \vspace{1.5cm}
      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_150.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_288.pdf} }
      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
\caption{3D channel flow (adaptive mesh): numerical simulation was performed with the smae boundary and initial conditions as in Figs.~\ref{fig:3DChannel_PermMesh}-\ref{fig:3DChannel_Isosurf} with an adaptive mesh. Flow pathway is very similar to the one shown in Fig.~\ref{fig:3DChannel_sat}.}
\label{fig:3DChannel_sat_adapt}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.5\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_60.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_90.pdf} }
      \hbox{\hspace{3.0cm} (a) t=0.29s \hspace{4.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
      \vspace{1.5cm}
      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_150.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_288.pdf} }
      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
\caption{3D channel flow (adaptive mesh): numerical simulation was performed with the same boundary and initial conditions as in Figs.~\ref{fig:3DChannel_PermMesh}-\ref{fig:3DChannel_Isosurf} with an adaptive mesh. Flow pathway is very similar to the one shown in Fig.~\ref{fig:3DChannel_sat}.}
\label{fig:3DChannel_sat_adapt}
\end{figure}
\end{landscape}
\clearpage
